%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Parsa Khavarinejad} \\ \vspace{1pt}
    Tehran, Iran \\ \vspace{1pt}
    \small \raisebox{-0.1\height}{\faPhone}\ +989036277666 ~ \href{mailto:parsa.khavarinejad@gmail.com}{\raisebox{-0.2\height}{\faEnvelope}\  \underline{Gmail}} ~ 
    \href{https://linkedin.com/in/parsa-khavarinejad}{\raisebox{-0.2\height}{\faLinkedin}\ \underline{LinkedIn}}  ~
    \href{https://github.com/parsakhavarinejad}{\raisebox{-0.2\height}{\faGithub}\ \underline{GitHub}} ~ \href{https://join.skype.com/invite/elXkdnvbtiRW}{\raisebox{-0.2\height}{\faSkype}\ \underline{Skype}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tarbiat Modares University}{Sep. 2022 - Present}
      {M.S. in Operations Research, GPA: 3.3/4}{Tehran, Iran}
      \resumeItemListStart
        \resumeItem{MSc Thesis: A Deep Learning Approach for Echocardiography Video Super-Resolution and Denoising.}
      \resumeItemListEnd

    \resumeSubheading
      {University of Tehran}{Sep. 2017 - Mar. 2022}
      {B.S. in Applied Mathematics, GPA of the last 2.5 years: 3.41/4}{Tehran, Iran}
      \resumeItemListStart
        \resumeItem{BSc Thesis: A Hybrid Deep Learning Approach for Stock Price Prediction.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-15pt}
%------Research Interests-------
\section{Research Interests}
    %\resumeSubHeadingListStart
        \begin{multicols}{3}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item Medical Image Processing
                \item Deep Learning
                \item Computer Vision
                %\item Time series analysis
                %\item Game Theory
                %\item Operations Research
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Attended Coursework}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Computer Science and Statistics} \emph{}}{}
            \begin{multicols}{4}
                \begin{itemize}[itemsep=-5pt, parsep=3pt]
                    \item\small Fundamentals of Computer Science and Programming
                    \item Advanced Programming
                    \item Deep Learning
                    \item Data Mining
                    \item Mathematical Laboratory 
                    \item Probability and Statistics
                    \item Multivariate Statistical Analysis
                    \item Design Of Experiments
                    \item Graph Theory
                    \item Combinatorics
                \end{itemize}
            \end{multicols}
            \vspace*{2.0\multicolsep}
        \resumeProjectHeading
          {\textbf{Operations Research and Optimization} \emph{}}{}
            \begin{multicols}{4}
                \begin{itemize}[itemsep=-5pt, parsep=3pt]
                    \item\small Linear Programming 1, 2
                    \item Non-Linear Programming
                    \item Integer Programming
                    \item Basic and Advanced Linear Algebra
                    \item Game Theory 1 and 2
                    \item Numerical Analysis
                    \item Queuing Theory
                    \item Facility Layout
                    \item Sequencing Theory
                    \item Engineering Economics
                \end{itemize}
            \end{multicols}
            \vspace*{2.0\multicolsep}
    \resumeSubHeadingListEnd
\vspace{-5pt}


%-----------Researches-----------
\section{Research}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Thesis: A Deep Learning Approach for Echocardiography Video Super-Resolution and Denoising}\emph{}}{Ongoing}
          \resumeItemListStart
            \resumeItem{Researching novel deep learning and GAN and Diffusion-based techniques for super-resolution of Echocardiography videos to advance medical imaging and enhance diagnostic precision.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Neuroimage Synthesis with Incomplete Multi-Modality Data}\emph{}}{Ongoing}
          \resumeItemListStart
            \resumeItem{Collaborating and researching with experts in neuroimaging to advance the synthesis of neuroimages with incomplete multi-modality data for comprehensive insights and improved medical diagnostics.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Seminar on the Application of AI in Echocardiography}\emph{}}{June 2023}
          \resumeItemListStart
            \resumeItem{Researched AI applications in echocardiography, analyzing insights from 40+ scholarly articles.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Modeling queuing theory for aircraft arrivals at a single airport} \emph{}}{July 2023}
          \resumeItemListStart
            \resumeItem{Researched queuing theory to optimize aircraft arrivals at an airport.}
          \resumeItemListEnd
          \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{Single machine scheduling to minimize earliness and tardiness costs} \emph{}}{Jan. 2023}
          \resumeItemListStart
            \resumeItem{Researched single-machine scheduling to minimize earliness and tardiness costs, optimizing scheduling efficiency.}
          \resumeItemListEnd 
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{A review of the p-facility median location problem} \emph{}}{Jan. 2023}
          \resumeItemListStart
            \resumeItem{Reviewed the p-facility median location problem, enhancing facility location optimization understanding.}
          \resumeItemListEnd 
          \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{Time-Series Models Research} \emph{}}{Dec. 2022}
          \resumeItemListStart
            \resumeItem{Explored diverse models like ARIMA, VARIMA, StatsForecastAutoArima, NHITSModel, TCNModel, TFTModel for regression trading, aiming to identify effective approaches for predicting special market trends.}
          \resumeItemListEnd 
          \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{Deception-based Game Theoretical Approach to Mitigate DoS Attacks} \emph{}}{May 2021}
          \resumeItemListStart
            \resumeItem{Researched on employing deception tactics within a game-theoretical framework to counter Denial-of-Service (DoS) attacks, providing innovative strategies to bolster cybersecurity.}
          \resumeItemListEnd 
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Using Game Theory for Los Angeles Airport Security}  \emph{}}{Jan. 2020}
          \resumeItemListStart
            \resumeItem{Conducted research on innovative Game Theory strategies to enhance security at Los Angeles International Airport.}
          \resumeItemListEnd 
     \resumeSubHeadingListEnd
     
%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Breast Cancer Image Segmentation and Classification} $|$ \emph{Python, Pytorch}}{Dec. 2023}
          \resumeItemListStart
            \resumeItem{Worked on a breast cancer image segmentation and classification project for the deep learning in healthcare course.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Breast Cancer Image Generation and Representation} $|$ \emph{Python, Pytorch}}{Dec. 2023}
          \resumeItemListStart
            \resumeItem{Worked on a breast cancer image generation using GAN and representation using AutoEncoder project for the deep learning in healthcare course.}
          \resumeItemListEnd
          \vspace{-13pt}
          
           \resumeProjectHeading
          {\textbf{TSP and mTSP Optimization Using Pyomo} $|$ \emph{Python, Pyomo}}{Dec. 2023}
          \resumeItemListStart
            \resumeItem{Coded the Traveling Salesman Problem (TSP) and Multi-TSP using Python and the Pyomo library.}
          \resumeItemListEnd 
          \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{Database Development for Crypto Exchange Data} $|$ \emph{Python, Postgresql, pgAdmin}}{April 2023}
          \resumeItemListStart
            \resumeItem{Developed a cryptocurrency database, implementing instance calculations for features such as OHLCV, candle derivatives, and technical indicators.}
          \resumeItemListEnd 
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Bank Marketing Analysis using Python} $|$ \emph{Python}}{July 2023}
          \resumeItemListStart
            \resumeItem{Accomplished Bank Marketing Analysis project using statistical techniques such as logistic regression, discriminant analysis, and PCA.}
          \resumeItemListEnd 
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Classification of Heart disease} $|$ \emph{Python, Scikit-Learn}}{Jan. 2023}
          \resumeItemListStart
            \resumeItem{Developed a heart disease classification system using machine learning for early detection and intervention.}
          \resumeItemListEnd 
          \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{A Heuristic Algorithm for Distributed and Flexible Jobshop Scheduling Problem} $|$ \emph{Python}}{Jan. 2023}
          \resumeItemListStart
            \resumeItem{Coded a Python heuristic for efficient Distributed and Flexible Jobshop Scheduling.}
          \resumeItemListEnd 
          \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{Electrocardiogram classification using one-dimensional CNN} $|$ \emph{Python, Tensorflow}}{Jan. 2022}
          \resumeItemListStart
            \resumeItem{Developed a project involving ECG classification using a one-dimensional CNN, showcasing deep learning's effectiveness in enhancing accuracy and diagnostic capabilities in ECG analysis.}
          \resumeItemListEnd 
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Renewable Energy Competition: Bayesian Cournot Games and Engineering Economic}  \emph{}}{June 2021}
          \resumeItemListStart
            \resumeItem{Explored the fusion of Bayesian Cournot Games and Engineering Economics in a Renewable Energy Competition, offering insights into strategic market dynamics and economic implications.}
          \resumeItemListEnd 
          \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{Data-stream mining} $|$ \emph{Python, Scikit-multiflow}}{Jan. 2021}
          \resumeItemListStart
            \resumeItem{Executed a data-stream mining project. Emphasizing classification and clustering for real-time analysis of dynamic data streams.}
          \resumeItemListEnd 
          \vspace{-10pt}
        \resumeProjectHeading
          {\textbf{Game Theory and the Export booms} \emph{}}{Jan. 2020}
          \resumeItemListStart
            \resumeItem{Explored the connection between Game Theory, Export Booms, and economic concepts, analyzing dynamics of export-driven economic growth.}
          \resumeItemListEnd 
          \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{Class Management App} $|$ \emph{Python, OOP, DataBase}}{Jan. 2021}
          \resumeItemListStart
            \resumeItem{Coded a comprehensive class management app designed for students, professors, and courses as part of the Advanced Python course.}
          \resumeItemListEnd
          \vspace{-13pt}
    \resumeSubHeadingListEnd
\vspace{-2pt}

%-----------TA-----------
\section{Teaching Experiences}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{Data Mining} $|$ \emph{Tarbiat Modares University}}{Fall 2023}
            \resumeItemListStart
                \resumeItem{Teaching Assistant, Dr. Toktam Khatibi}
            \resumeItemListEnd
            \vspace{-13pt}
        \resumeProjectHeading
            {\textbf{Calculus 2} $|$ \emph{University of Tehran}}{Winter 2020}
            \resumeItemListStart
                \resumeItem{Teaching Assistant, Dr. Gholamreza Rokni Lamouki}
            \resumeItemListEnd
            \vspace{-13pt}
        \resumeProjectHeading
            {\textbf{Differential Equation} $|$ \emph{University of Tehran}}{Fall 2020}
            \resumeItemListStart
                \resumeItem{Teaching Assistant, Dr. Gholamreza Rokni Lamouki}
            \resumeItemListEnd
            \vspace{-13pt}
        \resumeProjectHeading
            {\textbf{Game Theory 1} $|$ \emph{University of Tehran}}{Fall 2020}
            \resumeItemListStart
                \resumeItem{Teaching Assistant, Dr. MahdiReza Darvishzade}
            \resumeItemListEnd
            \vspace{-13pt}
        \resumeProjectHeading
            {\textbf{Calculus 1} $|$ \emph{University of Tehran}}{Fall 2020}
            \resumeItemListStart
                \resumeItem{Teaching Assistant, Dr. Gholamreza Rokni Lamouki}
            \resumeItemListEnd
            \vspace{-13pt}
        \resumeProjectHeading
            {\textbf{Calculus 1} $|$ \emph{University of Tehran}}{Fall 2019}
            \resumeItemListStart
                \resumeItem{Teaching Assistant, Dr. Gholamreza Rokni Lamouki}
            \resumeItemListEnd
            \vspace{-13pt}
        \resumeProjectHeading
            {\textbf{Differential Equation} $|$ \emph{University of Tehran}}{Fall 2019}
            \resumeItemListStart
                \resumeItem{Teaching Assistant, Dr. Gholamreza Rokni Lamouki}
            \resumeItemListEnd
            \vspace{-13pt}
    \resumeSubHeadingListEnd

\vspace{-5pt}
%
%-----------Presentations-----------
\section{Presentations}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{Disease-specific Neuroimage Synthesis with Incomplete Data.} $|$ \emph{University of Tehran}}{Dec. 2023}
    \resumeItemListStart
      \resumeItem{Explore "Disease-specific Neuroimage Synthesis" for precise diagnostics from incomplete data, uncovering transformative applications in medical imaging}
      \resumeItemListEnd 
      \vspace{-13pt}
    \resumeProjectHeading
        {\textbf{CNN and RNN Code Workshop} $|$ \emph{Tarbiat Modares University}}{Dec. 2023}
        \resumeItemListStart
          \resumeItem{Hosted a hands-on session on Convolutional and Recurrent Neural Network code using Keras for the Computer Vision class.}
          \resumeItemListEnd 
          \vspace{-13pt}
    \resumeProjectHeading
        {\textbf{EfficientNet V2} $|$ \emph{Tarbiat Modares University}}{Dec. 2023}
        \resumeItemListStart
          \resumeItem{Discussed EfficientNet V2, and its applications, and provided code examples.}
        \resumeItemListEnd 
        \vspace{-13pt}
    \resumeProjectHeading
          {\textbf{Seminar on the Application of AI in Echocardiography} $|$ \emph{Tarbiat Modares University}}{June 2023}
          \resumeItemListStart
            \resumeItem{Presented AI applications in echocardiography and discussed potential research directions for further advancements.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Time-Series models} $|$ \emph{Bitex, Accretive team}}{March 2023}
          \resumeItemListStart
            \resumeItem{Presented Temporal Convolutional Networks (TCNs) and Temporal Fusion Transformer (TFT) models, highlighting their architectures and diverse applications.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Introduction to Markov Chains} $|$ \emph{Tarbiat Modares University}}{June 2023}
          \resumeItemListStart
            \resumeItem{Presented Markov Chains basics in an easy-to-understand manner.}
          \resumeItemListEnd
          \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{Python for Data Mining} $|$ \emph{Tarbiat Modares University}}{March. 2023}
          \resumeItemListStart
            \resumeItem{Hosted a hands-on Python for Data Mining workshop.}
          \resumeItemListEnd 
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Electrocardiogram classification using one-dimensional CNN} $|$ \emph{University of Tehran}}{Jan. 2022}
          \resumeItemListStart
            \resumeItem{Presented 1D CNN's application in ECG data analysis, emphasizing its effectiveness in feature extraction for accurate interpretation.}
          \resumeItemListEnd 
          \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{Stone–Weierstrass Theorems} $|$ \emph{University of Tehran}}{Jan. 2020}
          \resumeItemListStart
            \resumeItem{Presented the Stone–Weierstrass Theorem, delving into its key aspects and implications within mathematics.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-13pt}

%-----------EXPERIENCE-----------
\section{Job Experiences}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AI Developer}{Aug. 2022 - Aug. 2023}
      {Bitex}{Tehran, Iran}
      \resumeItemListStart
        \resumeItem{Collaborated with experts to develop a crypto market AI trader bot, utilizing machine learning and data analysis,}
        \resumeItem{Researched time series machine learning algorithms to optimize trading models, achieving increased profitability.}
      \resumeItemListEnd

    \resumeSubheading
      {Co-Founder and Product Lead}{Sep. 2020 - Aug. 2022}
      {Nilwood}{Tehran, Iran}
      \resumeItemListStart
        \resumeItem{Co-founded Nilwood, a home and kitchen accessories company.}
        \resumeItem{Met market demands through accessory development.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-13pt}


% ----------Honours---------
\section{Honours and Awards}
    \resumeSubHeadingListStart
        \resumeSubheading{National University Entrance Exam for BSc}{2017}{}{}
        \vspace{-15pt}
        \resumeItemListStart
            \resumeItem{Ranked 613 out of almost 150,000 participants.}
            \resumeItem{Majoring in Maths and Physics}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
    \vspace{-13pt}
    \resumeSubHeadingListStart
        \resumeSubheading{National University Entrance Exam for MSc}{2022}{}{}
        \vspace{-15pt}
        \resumeItemListStart
            \resumeItem{Ranked 135 out of almost 10,000 participants.}
            \resumeItem{Majoring in Industrial Engineering}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

\vspace{-15pt}

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: English: Advanced, Persian: Native} \\
     \textbf{Development}{: Python, SQL, Github, Docker, Linux, Matlab} \\
     \textbf{AI}{: Scikit-Learn, Keras, TensorFlow, Pytorch, OpenCV} \\
     \textbf{Data Analysis and Visualization}{: Pandas, Numpy, Matplotlib, Seaborn, Minitab and SPSS, Power BI} \\
     \textbf{Document Preparation}{: \LaTeX, MS Office} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------References-----------
\section{References}
Available upon request
%    \resumeSubHeadingListStart
 %       \resumeSubheading{Toktam Khatibi}{}{Email: toktam.khatibi@modares.ac.ir}{}
  %  \resumeSubHeadingListEnd
   % \vspace{-13pt}
%    \resumeSubHeadingListStart
 %       \resumeSubheading{Hedieh Sajedi}{}{Email: hhsajedi@ut.ac.ir}{}
  %  \resumeSubHeadingListEnd
   % \vspace{-13pt}
%    \resumeSubHeadingListStart
 %       \resumeSubheading{Reza Baradaran Kazemzadeh}{}{Email: rkazem@modares.ac.ir}{}
  %  \resumeSubHeadingListEnd
   % \vspace{-13pt}
%    \resumeSubHeadingListStart
 %       \resumeSubheading{Gholam Reza Rokni Lamouki}{}{Email: rokni@ut.ac.ir}{}
  %  \resumeSubHeadingListEnd
%    \vspace{-13pt}
\vspace{-15pt}

\end{document}
